Improving real-time trend estimates using local parametrisation of polynomial regression filters

### 2024-02-12 article_jos.qmd
typos

:::: {.abstract}
This paper studies and compares real-time estimates of the trend-cycle component with moving averages based on local polynomial regression.
In particular, this theory allows to reproduce Henderson's symmetric and Musgrave's asymmetric filters.
This paper describes how they can be extended to include a timeliness criterion to minimise the phase shift.
While asymmetric filters are generally parametrised globally, which can be suboptimal around turning points, this paper proposes a procedure for parametrising them locally.
An empirical comparison, based on simulated and real data, shows that modelling polynomial trends that are too complex introduces more revisions without reducing the phase shift, and that local parametrisation reduces the delay in detecting turning points and reduces revisions.
The paper also shows how these results can be easily reproduced using the R package `rjd3filters` dedicated to the manipulation of moving averages.

@@

A moving average, or linear filter, is a statistical method that consists in applying a rolling weighted mean to a times series: for each date $t$ it computes a weighted mean of $p$ past points and $q$ future points where $p,q\geq0$ depends on the moving average.
Moving averages are ubiquitous in business cycle extraction and seasonal adjustment methods.
For example, the X-13ARIMA seasonal adjustment method uses several moving averages to estimate the main components of a time series. 
Symmetric filters are applied to the center of the series, but when it comes to estimate the most recent points, all of these methods must rely on asymmetric filters. 
For trend-cycle extraction, the most popular symmetric filter is the @henderson1916note moving average, which is used in the X-13ARIMA seasonal adjustment algorithm.

@@

Using local polynomial regression, @proietti2008 developed general class of symmetric and asymmetric moving averages.
In particular, it makes possible to reproduce Henderson's symmetric filter and Musgrave's asymmetric filters.
However, these methods have two drawbacks.
Firstly, the phase shift (i.e. the delay in detecting turning points) is not directly controlled.
Secondly, asymmetric filters depend on a parameter that is generally estimated over the whole series using assumptions that may be wrong locally.
The aim of this study is to propose extensions to the @proietti2008 class of filters in order to take these shortcomings into account.
The extensions have been implemented in the R `rjd3filters` package (available at <https://github.com/rjdemetra/rjd3filters>) and are therefore easily reusable.

@@

# Some properties on moving averages {#sec-propMM}

Lots of papers describe the definition and the properties of moving averages and linear filters, see for example @ch12HBSA. 
In this section we summarize some of the main results to understand the next sections.

Let $p$ et $f$ two integers, a moving average $M_{\boldsymbol\theta}$ or $M$ is defined by a set of coefficients $\boldsymbol\theta=\transp{\begin{pmatrix}\theta_{-p}&\cdots&\theta_{f}\end{pmatrix}}$ such as for all time series $X_t$:
$$
M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}.
$$

@@

To interpret the notions of gain and phase shift, it is useful to illustrate the effects of moving averages on harmonic series $X_t=\e^{-i\omega t}$ with $\omega\in[0,\pi]$.
The moving average $M_{\boldsymbol\theta}$ transforms $X_t$ into:
$$
Y_t = M_{\boldsymbol\theta}X_t = \sum_{k=-p}^{+f} \theta_k \e^{-i \omega (t+k)}
= \left(\sum_{k=-p}^{+f} \theta_k \e^{-i \omega k}\right)\cdot X_t.
$$
The function  $\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{-i \omega k}$ is called the *transfer function* or *frequency response function*.
The frequency response function can equivalently be defined as $\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{i \omega k}$ ou $\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{2\pi i \omega k}$.
It can be rewritten as:
$$
\Gamma_{\boldsymbol\theta}(\omega) = \rho_{\boldsymbol\theta}(\omega)\e^{i\varphi_{\boldsymbol\theta}(\omega)},
$$
where  $\rho_{\boldsymbol\theta}(\omega)=G_{\boldsymbol\theta}(\omega)=\lvert\Gamma_{\boldsymbol\theta}(\omega)\rvert$ is the *gain* or *amplitude* function and $\varphi_{\boldsymbol\theta}(\omega)$ is the *phase shift* or *time shift* function.
This function is sometimes represented as $\phi_{\boldsymbol\theta}(\omega)=\frac{\varphi_{\boldsymbol\theta}(\omega)}{\omega}$ to mesure the phase shift in number of periods.
For all symmetric moving average we have $\varphi_{\boldsymbol\theta}(\omega)\equiv 0 \;(modulo\;{\pi})$.

@@

Fourier decomposition allows to analyze any time series as a sum of harmonic series, and each component (trend, cycle, seasonal, irregular) is associated with a set of frequencies.
Noting $\omega = 2\pi/p$, the harmonic series of frequency $\omega$ represents a series that repeats itself every $p$ periods.
For example, for a monthly series (12 observations per year), seasonal movements are those that repeat every year: they are therefore associated with frequencies $2\pi/12$ (annual periodicity), $2\pi/12\times 2=2\pi/6,\dots,2\pi/12\times 5$.
In this paper, we consider that the trend-cycle is associated with frequencies in the interval $[0, 2\pi/12[$, i.e. movements recurring at least every 12 months.
Even if different frequencies are sometimes used (e.g. $[0, 2\pi/36]$ to consider only cycles of at least 36 months), this has no impact on the results of the study.
The other frequencies, $[2\pi/12, \pi]$ are associated with the irregular component (undesirable oscillations).

@fig-graphsmusgrave shows the gain and phase shift function for the asymmetric Musgrave filter (see @sec-lppasymf) often used for real-time trend-cycle estimation (i.e. when no point in the future is known).
The gain function is greater than 1 on the frequencies associated with the trend-cycle ($[0, 2\pi/12]$): this means that the trend-cycle is well preserved and that short cycles of 1 to 2 years ($[2\pi/24,2\pi/12]$) are even amplified.
However, cycles of 8 to 12 months ($[2\pi/12, 2\pi/8]$), considered undesirable because associated with the irregular, are also amplified: this can lead to the detection of false turning points.
At other frequencies, the gain function is less than 1, but always positive: this means that the series smoothed by this moving average will always contain noise, even if it is attenuated.
Analysis of the phase shift shows that the shorter the cycles, the greater the phase shift: this means that on series smoothed by this moving average, turning points could be detected at the wrong date.

@@

Trend-cycles are generally modelled by local polynomial trends (see @sec-nonparamreg).
In order to best preserve the trend-cycles, we try to have moving averages that preserve the polynomial trends.
A moving average $M_{\boldsymbol\theta}$ preserves a function of time $f(t)$ if $\forall t:M_{\boldsymbol\theta} f(t)=f(t)$.

@@

- To preserve linear trends $X_t=at+b$ we need:
$$
\forall t:\:M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}=\sum_{k=-p}^{+f}\theta_k[a(t+k)+b]=a\sum_{k=-p}^{+f}k\theta_k+(at+b)\sum_{k=-p}^{+f}\theta_k=at+b.
$$
Which is equivalent to:
$$
\sum_{k=-p}^{+f}\theta_k=1
\quad\text{et}\quad
\sum_{k=-p}^{+f}k\theta_k=0.
$$
- In general, $M_{\boldsymbol\theta}$ preserves polynomials of degree $d$ if and only if:
$$
\sum_{k=-p}^{+f}\theta_k=1
 \text{ and }
\forall j \in \left\llbracket 1,d\right\rrbracket:\:
\sum_{k=-p}^{+f}k^j\theta_k=0.
$$
- If $M_{\boldsymbol\theta}$ is symmetric ($p=f$ and $\theta_{-k} = \theta_k$) and preserves polynomials of degree $2d$ then it also preserves polynomials of degree $2d+1$.

@@

Indeed, let $\{\varepsilon_t\}$ a sequence of independent random variables with $\E{\varepsilon_t}=0$, $\V{\varepsilon_t}=\sigma^2$:
$$
\V{M_{\boldsymbol\theta}\varepsilon_t}=\V{\sum_{k=-p}^{+f} \theta_k \varepsilon_{t+k}}
= \sum_{k=-p}^{+f} \theta_k^2 \V{\varepsilon_{t+k}}=
\sigma^2\sum_{k=-p}^{+f} \theta_k^2.
$$

@@

For symmetric filters, the phase shift function is equal to zero (modulo $\pi$).
So there is no delay in detecting turning points.
However, they cannot be used in the beginning and in the end of the time series because no past or future value can be used. 
Thus, for real-time estimation, it is needed to build asymmetric moving average that approximate the symmetric moving average.

@@

2. Apply symmetric filters to extended forecast series.
This method seems to date back to @deforest1877adjustment, which also suggests modelling a polynomial trend of degree three or less at the end of the period:\
"*As the first $m$ and last $m$ terms of the series cannot be reached directly by the formula, the series should be graphically extended by m terms at both ends, first plotting the observations on paper as ordinates, and then extending the curve along what seems to be its probable course, and measuring the ordinates of the extended portions.*
*It is not necessary that this extension should coincide with what would be the true course of the curve in those parts. *
*The important point is that the m terms thus added, taken together with the $m+1$ adjacent given terms, should follow a curve whose form is approximately algebraic and of a degree not higher than the third.*"\
This is also the approach used in the X-13ARIMA seasonal adjustment method, which extends which extends the series by one year with an ARIMA model.

@@

Conversely, the implicit forecasts of an asymmetric moving average can be deduced from a reference symmetric moving average. 
This allows to judge the quality of real-time estimates of the trend-cycle and to anticipate future revisions when forecasts are far from expected evolutions.\
Let us denote $v=(v_{-h},\dots, v_{h})$ the reference symmetric moving average and $w^0,\dots w^{h-1}$ a sequence of asymmetric moving averages, of order $h+1$ to $2h$ used to estimate the last $h$ points with, for convention, $w_t^q=0$ for $t>q$.
This means that $w^0=(w_{-h}^0,\dots, w_{0}^0)$ is used for estimation in real time (when no points are known in the future), $w^1=(w_{-h}^1,\dots, w_{1}^1)$ for estimation of the penultimate point (when only one point is known in the future), and so on.
Let also note $y_{-h},\dots,y_{0}$ the observed series studied and $y_{1}^*,\dots y_h^*$ the implicit forecast induced by $w^0,\dots w^{h-1}$.
This means that for all $q$ we have:
$$
\forall q, \quad \underbrace{\sum_{i=-h}^0 v_iy_i + \sum_{i=1}^h v_iy_i^*}_{\text{smoothing by }v\text{ of the extended series}}
=\underbrace{\sum_{i=-h}^0 w_i^qy_i + \sum_{i=1}^h w_i^qy_i^*}_{\text{smoothing by }w^q\text{ of the extended series}}.
$$
This is equivalent to:
$$
\forall q, \quad \sum_{i=1}^h (v_i- w_i^q) y_i^*
=\sum_{i=-h}^0 (w_i^q-v_i)y_i.
$$
To sum up, in matrix form, this is equivalent to solving:
$$
\scriptstyle
\begin{pmatrix}
  v_1 & v_2 & \cdots & v_h \\
  v_1 - w_1^1 & v_2 & \cdots & v_h \\
  \vdots & \vdots & \cdots & \vdots \\
   v_1 - w_1^{h-1} & v_2-w_2^{h-1} & \cdots & v_h
\end{pmatrix}
\begin{pmatrix}y_1^* \\ \vdots \\ y_h^*\end{pmatrix}=
\begin{pmatrix}
  w_{-h}^0 - v_{-h} & w_{-(h-1)}^0 - v_{-(h-1)} & \cdots & w_{0}^0 - v_{0} \\
  w_{-h}^1 - v_{-h} & w_{-(h-1)}^1 - v_{-(h-1)} & \cdots & w_{0}^1 - v_{0} \\
  \vdots & \vdots & \cdots & \vdots \\
  w_{-h}^{h-1} - v_{-h} & w_{-(h-1)}^{h-1} - v_{-(h-1)} & \cdots & w_{0}^{h-1} - v_{0}
\end{pmatrix}
\begin{pmatrix}y_{-h} \\ \vdots \\ y_0\end{pmatrix}.
$$
This is implemented in the `rjd3filters::implicit_forecast()` function.

@@

@ch15HBSA propose a general approach to derive linear filters, based on an optimisation problem involving three criteria: *Fidelity* ($F_g$), *Smoothness* ($S_g$) and *Timeliness* ($T_g$).
Fidelity can be directly linked to the reduction in variance created by the filter, and timeliness to the notion of phase shift, which again we want to be low. 
This method can be used inR with the function `rjd3filters::fst_filter()`.

@@

```{=tex}
\begin{table}[!h]
\caption{\label{tab-QC} Quality criteria for asymmetric filters ($q=0,1,2$) computed by local polynomials using the Henderson kernel with $h=6$ and $R=3,5$.}
{\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{ccc}
\toprule
Code & Description & Formula\\
\midrule
$b_c$ & Constant bias & $\sum_{k=-p}^{+f}\theta_{k}-1$\\
$b_l$ & Linear bias & $\sum_{k=-p}^{+f}k\theta_{k}$\\
$b_q$ & Quadratic bias & $\sum_{k=-p}^{+f}k^{2}\theta_{k}$\\
$F_g$ & Variance reduction / Fidelity (Guggemos) & $\sum_{k=-p}^{+f}\theta_{k}^{2}$\\
$S_g$ & Smoothness (Guggemos) & $\sum_{j}(\nabla^{3}\theta_{j})^{2}$\\
\addlinespace
$T_g$ & Timeliness (Guggemos) & $\int_{0}^{\omega_1}\rho_{\boldsymbol\theta}(\omega)\sin(\varphi_{\boldsymbol\theta}(\omega))^{2}\ud\omega$\\
$A_w$ & Accuracy (Wildi) & $2\int_0^{\omega_1}\left(\rho_{s}(\omega)-\rho_{\boldsymbol\theta}(\omega)\right)^{2}h(\omega)\ud\omega$\\
$T_w$ & Timeliness (Wildi) & $8\int_0^{\omega_1} \rho_{s}(\omega)\rho_{\boldsymbol\theta}(\omega)\sin^{2}\left(\frac{\varphi_s(\omega)-\varphi_{\boldsymbol\theta}(\omega)}{2}\right)h(\omega)\ud\omega$\\
$S_w$ & Smoothness (Wildi) & $2\int_{\omega_1}^{\pi}\left(\rho_{s}(\omega)-\rho_{\boldsymbol\theta}(\omega)\right)^{2}h(\omega)\ud\omega$\\
$R_w$ & Residual (Wildi) & $8\int_{\omega_1}^{\pi} \rho_{s}(\omega)\rho_{\boldsymbol\theta}(\omega)\sin^{2}\left(\frac{\varphi_s(\omega)-\varphi_{\boldsymbol\theta}(\omega)}{2}\right)h(\omega)\ud\omega$\\
\bottomrule
\end{tabular}}}

@@

In practice, this means assuming that the trend is locally polynomial. 
Various estimation methods can be used to derive symmetric and asymmetric moving averages.  
@GrayThomson1996 propose a complete statistical framework which makes it possible, in particular, to model the error in approximating the trend by local polynomials.
However, as the specification of this error is generally complex, simpler models may be preferred, such as that of @proietti2008.  
Finally, @dagumbianconcini2008 propose a similar modelling of the trend-cycle but using the theory of Hilbert spaces with reproducing kernels for estimation, which has the particular advantage of facilitating the calculation of different moving averages at different time frequencies.
This method can be used inR with the function `rjd3filters::rkhs_filter()`.

@@

To estimate $\boldsymbol \beta$ we need $2h+1\geq d+1$ and the estimation is made by weighted least squares (WLS), which is equivalent to minimising the following objective function:
$$
S(\hat{\beta}_{0},\dots,\hat{\beta}_{d})=\sum_{j=-h}^{h}\kappa_{j}(y_{t+j}-\hat{\beta}_{0}-\hat{\beta}_{1}j-\dots-\hat{\beta}_{d}j^{d})^{2}.
$$
where $\kappa_j$ is a set of weights called *kernel*.
We have $\kappa_j\geq 0:\kappa_{-j}=\kappa_j$, and with $\boldsymbol K=diag(\kappa_{-h},\dots,\kappa_{h})$, the estimate of $\boldsymbol \beta$ can be written as $\hat{\boldsymbol\beta}=(\boldsymbol X'\boldsymbol K\boldsymbol X)^{-1}\boldsymbol X'\boldsymbol K\boldsymbol y.$
With $\boldsymbol e_1=\transp{\begin{pmatrix}1 &0 &\cdots&0 \end{pmatrix}}$, the estimate of the trend is:
$$
\hat{m}_{t}=\boldsymbol e_{1}\hat{\boldsymbol \beta}=\boldsymbol \theta'\boldsymbol y=\sum_{j=-h}^{h}\theta_{j}y_{t-j}\text{ with }\boldsymbol \theta=\boldsymbol K\boldsymbol X(\boldsymbol X'\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{1}.
$$ {#eq-mmsym}
To conclude, the estimate of the trend $\hat{m}_{t}$ can be obtained applying the symmetric filter $\boldsymbol \theta$ to $y_t$ ($\boldsymbol \theta$ is symmetric due to the symmetry of the kernel weights $\kappa_j$).
Moreover, $\boldsymbol X'\boldsymbol \theta=\boldsymbol e_{1}$ so:
$$
\sum_{j=-h}^{h}\theta_{j}=1,\quad\forall r\in\left\llbracket 1,d\right\rrbracket:\sum_{j=-h}^{h}j^{r}\theta_{j}=0.
$$
Hence, the filter $\boldsymbol w$ preserve deterministic polynomial of order $d$.

@@

```{r echo = FALSE}
#| label: tab-criteraLp
#| eval: false
#| tab-cap: 
title <- "Quality criteria for asymmetric filters ($q=0,1,2$) computed by local polynomials using the Henderson kernel with $h=6$ and $R=3,5$."

@@

# R code example {#ann-ex-r}

>>>>

:::: {.abstract}
This paper studies and compares real-time estimates of the trend-cycle component with moving averages based on local polynomial regression.
In particular, this theory allows us to reproduce Henderson's symmetric and Musgrave's asymmetric filters.
This paper describes how they can be extended to include a timeliness criterion to minimise the phase shift.
While asymmetric filters are generally parametrised globally, which can be suboptimal around turning points, this paper proposes a procedure for parametrising them locally.
An empirical comparison, based on simulated and real data, shows that modelling polynomial trends that are too complex introduces more revisions without reducing the phase shift, and that local parametrisation reduces the delay in detecting turning points and reduces revisions.
The paper also shows how these results can be easily reproduced using the R package `rjd3filters` dedicated to the manipulation of moving averages.

@@

A moving average, or linear filter, is a statistical method that consists of applying a rolling weighted mean to a times series: for each date $t$ it computes a weighted mean of $p$ past points and $q$ future points where $p,q\geq0$ depends on the moving average.
Moving averages are ubiquitous in business cycle extraction and seasonal adjustment methods.
For example, the X-13ARIMA seasonal adjustment method uses several moving averages to estimate the main components of a time series. 
Symmetric filters are applied to the center of the series, but when it comes to estimate the most recent points, all of these methods must rely on asymmetric filters. 
For trend-cycle extraction, the most popular symmetric filter is the @henderson1916note moving average, which is used in the X-13ARIMA seasonal adjustment algorithm.

@@

Using local polynomial regression, @proietti2008 developed a general class of symmetric and asymmetric moving averages.
In particular, it becomes possible to reproduce Henderson's symmetric filter and Musgrave's asymmetric filters.
However, these methods have two drawbacks.
Firstly, the phase shift (i.e. the delay in detecting turning points) is not directly controlled.
Secondly, asymmetric filters depend on a parameter that is generally estimated over the whole series using assumptions that may be wrong locally.
The aim of this study is to propose extensions to the @proietti2008 class of filters in order to take these shortcomings into account.
The extensions have been implemented in the R `rjd3filters` package (available at <https://github.com/rjdemetra/rjd3filters>) and are therefore easily reusable.

@@

# Some properties of moving averages {#sec-propMM}

Numerous papers describe the definition and the properties of moving averages and linear filters, see for example @ch12HBSA. 
In this section we summarize some of the main results to understand the next sections.

Let $p$ and $f$ two integers, a moving average $M_{\boldsymbol\theta}$ or $M$ is defined by a set of coefficients $\boldsymbol\theta=\transp{\begin{pmatrix}\theta_{-p}&\cdots&\theta_{f}\end{pmatrix}}$ such as for all time series $X_t$:
$$
M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}.
$$

@@

To interpret the notions of gain and phase shift, it is useful to illustrate the effects of moving averages on harmonic series $X_t=\e^{-i\omega t}$ with $\omega\in[0,\pi]$.
The moving average $M_{\boldsymbol\theta}$ transforms $X_t$ into:
$$
Y_t = M_{\boldsymbol\theta}X_t = \sum_{k=-p}^{+f} \theta_k \e^{-i \omega (t+k)}
= \left(\sum_{k=-p}^{+f} \theta_k \e^{-i \omega k}\right)\cdot X_t.
$$
The function  $\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{-i \omega k}$ is called the *transfer function* or *frequency response function*.
The frequency response function can alternatively be defined as $\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{i \omega k}$ or $\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{2\pi i \omega k}$.
It can be rewritten as:
$$
\Gamma_{\boldsymbol\theta}(\omega) = \rho_{\boldsymbol\theta}(\omega)\e^{i\varphi_{\boldsymbol\theta}(\omega)},
$$
where  $\rho_{\boldsymbol\theta}(\omega)=G_{\boldsymbol\theta}(\omega)=\lvert\Gamma_{\boldsymbol\theta}(\omega)\rvert$ is the *gain* or *amplitude* function and $\varphi_{\boldsymbol\theta}(\omega)$ is the *phase shift* or *time shift* function.
This function is sometimes represented as $\phi_{\boldsymbol\theta}(\omega)=\frac{\varphi_{\boldsymbol\theta}(\omega)}{\omega}$ to measure the phase shift in number of periods.
For all symmetric moving averages we have $\varphi_{\boldsymbol\theta}(\omega)\equiv 0 \;(modulo\;{\pi})$.

@@

Fourier decomposition allows us to analyze any time series as a sum of harmonic series, and each component (trend, cycle, seasonal, irregular) is associated with a set of frequencies.
Noting $\omega = 2\pi/p$, the harmonic series of frequency $\omega$ represents a series that repeats itself every $p$ periods.
For example, for a monthly series (12 observations per year), seasonal movements are those that repeat every year: they are therefore associated with frequencies $2\pi/12$ (annual periodicity), $2\pi/12\times 2=2\pi/6,\dots,2\pi/12\times 5$.
In this paper, we consider that the trend-cycle is associated with frequencies in the interval $[0, 2\pi/12]$, i.e. movements recurring at least every 12 months.
Even if different frequencies are sometimes used (e.g. $[0, 2\pi/36]$ to consider only cycles of at least 36 months), this has no impact on the results of the study.
The other frequencies, $[2\pi/12, \pi]$ are associated with the irregular component (undesirable oscillations).

@fig-graphsmusgrave shows the gain and phase shift function for the asymmetric Musgrave filter (see @sec-lppasymf) often used for real-time trend-cycle estimation (i.e. when no point in the future is known).
The gain function is greater than 1 on the frequencies associated with the trend-cycle ($[0, 2\pi/12]$): this means that the trend-cycle is well preserved and that short cycles of 1 to 2 years ($[2\pi/24,2\pi/12]$) are even amplified.
At other frequencies, the gain function is less than 1, but always positive: this means that the series smoothed by this moving average will always contain noise, even if it is attenuated.
Analysis of the phase shift shows that the shorter the cycles, the greater the phase shift: this means that on series smoothed by this moving average, turning points could be detected at the wrong date.

@@

Trend-cycles are generally modelled by local polynomial trends (see @sec-nonparamreg).
In order to best preserve the trend-cycles, we try to design moving averages that preserve the polynomial trends.
A moving average $M_{\boldsymbol\theta}$ preserves a function of time $f(t)$ if $\forall t:M_{\boldsymbol\theta} f(t)=f(t)$.

@@

- To preserve linear trends $X_t=at+b$ we need:
$$
\forall t:\:M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}=\sum_{k=-p}^{+f}\theta_k[a(t+k)+b]=a\sum_{k=-p}^{+f}k\theta_k+(at+b)\sum_{k=-p}^{+f}\theta_k=at+b.
$$
Which is equivalent to:
$$
\sum_{k=-p}^{+f}\theta_k=1
\quad\text{and}\quad
\sum_{k=-p}^{+f}k\theta_k=0.
$$
- In general, $M_{\boldsymbol\theta}$ preserves polynomials of degree $d$ if and only if:
$$
\sum_{k=-p}^{+f}\theta_k=1
 \text{ and }
\forall j \in \left\llbracket 1,d\right\rrbracket:\:
\sum_{k=-p}^{+f}k^j\theta_k=0.
$$
- If $M_{\boldsymbol\theta}$ is symmetric ($p=f$ and $\theta_{-k} = \theta_k$) and preserves polynomials of degree $2d$ then it also preserves polynomials of degree $2d+1$.

@@

Indeed, let $\{\varepsilon_t\}$ be a sequence of independent random variables with $\E{\varepsilon_t}=0$, $\V{\varepsilon_t}=\sigma^2$:
$$
\V{M_{\boldsymbol\theta}\varepsilon_t}=\V{\sum_{k=-p}^{+f} \theta_k \varepsilon_{t+k}}
= \sum_{k=-p}^{+f} \theta_k^2 \V{\varepsilon_{t+k}}=
\sigma^2\sum_{k=-p}^{+f} \theta_k^2.
$$

@@

For symmetric filters, the phase shift function is equal to zero (modulo $\pi$).
So there is no delay in detecting turning points.
However, they cannot be used in the beginning and in the end of the time series because no past or future value can be used. 
Thus, for real-time estimation, it is needed to build asymmetric moving averages that approximate the symmetric moving average.

@@

2. Apply symmetric filters to extended forecast series.
This method seems to date back to @deforest1877adjustment, which also suggests modelling a polynomial trend of degree three or less at the end of the period:\
"*As the first $m$ and last $m$ terms of the series cannot be reached directly by the formula, the series should be graphically extended by m terms at both ends, first plotting the observations on paper as ordinates, and then extending the curve along what seems to be its probable course, and measuring the ordinates of the extended portions.*
*It is not necessary that this extension should coincide with what would be the true course of the curve in those parts. *
*The important point is that the m terms thus added, taken together with the $m+1$ adjacent given terms, should follow a curve whose form is approximately algebraic and of a degree not higher than the third.*"\
This is also the approach used in the X-13ARIMA seasonal adjustment method, which extends the series by one year with an ARIMA model.

@@

Conversely, the implicit forecasts of an asymmetric moving average can be deduced from a reference symmetric moving average. 
This allows us to judge the quality of real-time estimates of the trend-cycle and to anticipate future revisions when forecasts are far from expected evolutions.\
Let us denote $v=(v_{-h},\dots, v_{h})$ the reference symmetric moving average and $w^0,\dots w^{h-1}$ a sequence of asymmetric moving averages, of order $h+1$ to $2h$ used to estimate the last $h$ points with, for convention, $w_t^q=0$ for $t>q$.
This means that $w^0=(w_{-h}^0,\dots, w_{0}^0)$ is used for estimation in real time (when no points are known in the future), $w^1=(w_{-h}^1,\dots, w_{1}^1)$ for estimation of the penultimate point (when only one point is known in the future), and so on.
Let also note $y_{-h},\dots,y_{0}$ the observed series studied and $y_{1}^*,\dots y_h^*$ the implicit forecast induced by $w^0,\dots w^{h-1}$.
This means that for all $q$ we have:
$$
\underbrace{\sum_{i=-h}^0 v_iy_i + \sum_{i=1}^h v_iy_i^*}_{\text{smoothing by }v\text{ of the extended series}}
=\underbrace{\sum_{i=-h}^0 w_i^qy_i + \sum_{i=1}^h w_i^qy_i^*}_{\text{smoothing by }w^q\text{ of the extended series}}.
$$
This is equivalent to:
$$
\quad \sum_{i=1}^h (v_i- w_i^q) y_i^*
=\sum_{i=-h}^0 (w_i^q-v_i)y_i.
$$
To sum up, in matrix form, this is equivalent to solving:
$$
\scriptstyle
\begin{pmatrix}
  v_1 & v_2 & \cdots & v_h \\
  v_1 - w_1^1 & v_2 & \cdots & v_h \\
  \vdots & \vdots & \cdots & \vdots \\
   v_1 - w_1^{h-1} & v_2-w_2^{h-1} & \cdots & v_h
\end{pmatrix}
\begin{pmatrix}y_1^* \\ \vdots \\ y_h^*\end{pmatrix}=
\begin{pmatrix}
  w_{-h}^0 - v_{-h} & w_{-(h-1)}^0 - v_{-(h-1)} & \cdots & w_{0}^0 - v_{0} \\
  w_{-h}^1 - v_{-h} & w_{-(h-1)}^1 - v_{-(h-1)} & \cdots & w_{0}^1 - v_{0} \\
  \vdots & \vdots & \cdots & \vdots \\
  w_{-h}^{h-1} - v_{-h} & w_{-(h-1)}^{h-1} - v_{-(h-1)} & \cdots & w_{0}^{h-1} - v_{0}
\end{pmatrix}
\begin{pmatrix}y_{-h} \\ \vdots \\ y_0\end{pmatrix}.
$$
This is implemented in the `rjd3filters::implicit_forecast()` function.

@@

@ch15HBSA propose a general approach to derive linear filters, based on an optimisation problem involving three criteria: *Fidelity* ($F_g$), *Smoothness* ($S_g$) and *Timeliness* ($T_g$).
Fidelity can be directly linked to the reduction in variance created by the filter, and timeliness to the notion of phase shift, which again we want to be low. 
This method can be used in R with the function `rjd3filters::fst_filter()`.

@@

```{=tex}
\begin{table}[!h]
\caption{\label{tab-QC} Quality criteria for asymmetric filters ($q=0,1,2$) computed by local polynomials using the Henderson kernel with $h=6$ and $R=3.55$.}
{\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{ccc}
\toprule
Code & Description & Formula\\
\midrule
$b_c$ & Constant bias & $\sum_{k=-p}^{+f}\theta_{k}-1$\\
$b_l$ & Linear bias & $\sum_{k=-p}^{+f}k\theta_{k}$\\
$b_q$ & Quadratic bias & $\sum_{k=-p}^{+f}k^{2}\theta_{k}$\\
$F_g$ & Variance reduction / Fidelity (Guggemos) & $\sum_{k=-p}^{+f}\theta_{k}^{2}$\\
$S_g$ & Smoothness (Guggemos) & $\sum_{j}(\nabla^{3}\theta_{j})^{2}$\\
\addlinespace
$T_g$ & Timeliness (Guggemos) & $\int_{0}^{\omega_1}\rho_{\boldsymbol\theta}(\omega)\sin(\varphi_{\boldsymbol\theta}(\omega))^{2}\ud\omega$\\
$A_w$ & Accuracy (Wildi) & $2\int_0^{\omega_1}\left(\rho_{s}(\omega)-\rho_{\boldsymbol\theta}(\omega)\right)^{2}h(\omega)\ud\omega$\\
$T_w$ & Timeliness (Wildi) & $8\int_0^{\omega_1} \rho_{s}(\omega)\rho_{\boldsymbol\theta}(\omega)\sin^{2}\left(\frac{\varphi_s(\omega)-\varphi_{\boldsymbol\theta}(\omega)}{2}\right)h(\omega)\ud\omega$\\
$S_w$ & Smoothness (Wildi) & $2\int_{\omega_1}^{\pi}\left(\rho_{s}(\omega)-\rho_{\boldsymbol\theta}(\omega)\right)^{2}h(\omega)\ud\omega$\\
$R_w$ & Residual (Wildi) & $8\int_{\omega_1}^{\pi} \rho_{s}(\omega)\rho_{\boldsymbol\theta}(\omega)\sin^{2}\left(\frac{\varphi_s(\omega)-\varphi_{\boldsymbol\theta}(\omega)}{2}\right)h(\omega)\ud\omega$\\
\bottomrule
\end{tabular}}}

@@

In practice, this means assuming that the trend is locally polynomial. 
Various estimation methods can be used to derive symmetric and asymmetric moving averages.  
@GrayThomson1996 propose a complete statistical framework that makes it possible, in particular, to model the error in approximating the trend by local polynomials.
However, as the specification of this error is generally complex, simpler models may be preferred, such as that of @proietti2008.  
Finally, @dagumbianconcini2008 propose a similar modelling of the trend-cycle but using the theory of Hilbert spaces with reproducing kernels for estimation, which has the particular advantage of facilitating the calculation of different moving averages at different time frequencies,
this method can be used in R with the function `rjd3filters::rkhs_filter()`.

@@

To estimate $\boldsymbol \beta$ we need at least $d+1$ observations (thus $2h\geq d$) and the estimation is made by weighted least squares (WLS), which is equivalent to minimising the following objective function:
$$
S(\hat{\beta}_{0},\dots,\hat{\beta}_{d})=\sum_{j=-h}^{h}\kappa_{j}(y_{t+j}-\hat{\beta}_{0}-\hat{\beta}_{1}j-\dots-\hat{\beta}_{d}j^{d})^{2}.
$$
where $\kappa_j$ is a set of weights called a *kernel*.
We have $\kappa_j\geq 0:\kappa_{-j}=\kappa_j$, and with $\boldsymbol K=diag(\kappa_{-h},\dots,\kappa_{h})$, the estimate of $\boldsymbol \beta$ can be written as $\hat{\boldsymbol\beta}=(\boldsymbol X'\boldsymbol K\boldsymbol X)^{-1}\boldsymbol X'\boldsymbol K\boldsymbol y.$
With $\boldsymbol e_1=\transp{\begin{pmatrix}1 &0 &\cdots&0 \end{pmatrix}}$, the estimate of the trend is:
$$
\hat{m}_{t}=\boldsymbol e_{1}\hat{\boldsymbol \beta}=\boldsymbol \theta'\boldsymbol y=\sum_{j=-h}^{h}\theta_{j}y_{t-j}\text{ with }\boldsymbol \theta=\boldsymbol K\boldsymbol X(\boldsymbol X'\boldsymbol K\boldsymbol X)^{-1}\boldsymbol e_{1}.
$$ {#eq-mmsym}
To conclude, the estimate of the trend $\hat{m}_{t}$ can be obtained applying the symmetric filter $\boldsymbol \theta$ to $y_t$ ($\boldsymbol \theta$ is symmetric due to the symmetry of the kernel weights $\kappa_j$).
Moreover, $\boldsymbol X'\boldsymbol \theta=\boldsymbol e_{1}$ so:
$$
\sum_{j=-h}^{h}\theta_{j}=1,\quad\forall r\in\left\llbracket 1,d\right\rrbracket:\sum_{j=-h}^{h}j^{r}\theta_{j}=0.
$$
Hence, the filter $\boldsymbol w$ preserves deterministic polynomials of order $d$.

@@

```{r echo = FALSE}
#| label: tab-criteraLp
#| eval: false
#| tab-cap: 
title <- "Quality criteria for asymmetric filters ($q=0,1,2$) computed by local polynomials using the Henderson kernel with $h=6$ and $R=3.5$."

@@

# R code example {#sec-ann-ex-r}
